An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-28 VLDB2026/main.tex
Update main.tex

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}. It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}

@@

	\textcolor{blue}{
	WinFilter maintains optimal performance by building an index for each tree node. It then performs an Approximate Nearest Neighbor (ANN) search on the relevant nodes and post-filters the results, ensuring high recall and queries per second (QPS).
	In contrast, iRange dynamically constructs a search graph during query time. This method has low overhead and performs well in small-range queries, but its performance degrades as the query range increases.
	UNIFY utilizes a skip list for localization followed by a linear scan for searching in small-range query scenarios. Its performance is generally lower than graph-based structures like iRange in these cases.
	Interestingly, Faiss, aided by its efficient ID selector for filtering, calculates distances for only a small subset of points in small-range scenarios. Consequently, it can outperform algorithms specifically designed for range searches.
	}
%	WinFilter consistently delivers the best performance. This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
%	
%	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes. In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios. However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.

>>>>

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:attribute-cross-platform}. It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values.}

@@

	\textcolor{blue}{
	WinFilter maintains optimal performance by building an index for each tree node. It then performs an ANN search on the relevant nodes and post-filters the results, ensuring high recall and QPS.
	In contrast, iRange dynamically constructs a search graph during query time. This method has low overhead and performs well in small-range queries, but its performance degrades as the query range increases.
	UNIFY utilizes a skip list for localization followed by a linear scan for searching in small-range query scenarios. Its performance is generally lower than graph-based structures like iRange in these cases.
	Interestingly, Faiss, aided by its efficient ID selector for filtering, calculates distances for only a small subset of points in small-range scenarios. Consequently, it can outperform algorithms specifically designed for range searches.
	}
%	WinFilter consistently delivers the best performance. This highlights its robustnes, which performs ANN search over only relevant tree nodes and merges results efficiently, making it highly effective for static range query scenarios.
%	
%	iRange offers a good balance between query efficiency and recall, demonstrating stable performance across both datasets and range sizes. In contrast, UNIFY experiences a notable drop in performance under narrow query ranges, suggesting that its HSIG structure—despite incorporating skip lists for pre-filtering—still has limitations in such scenarios. However, by leveraging HNSW and bitmap-based post-filtering, UNIFY performs competitively under broader range conditions, demonstrating strong scalability.
